Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-12-13 paper.tex
Add uncertainty analysis section; resolves #48

>>>>

\subsection{Uncertainty Analysis}

Uncertainty was considered from a combination of systematic and random errors.
The random error was inferred from the sample standard deviation (on a
per-revolution basis) and the systematic from the sensor calibrations or
datasheets. Combining both sources of error, along with their propagation into
quantities derived from multiple measurements, followed the procedures outlined
in Coleman and Steele \cite{ColemanSteele}, described below.

An expanded uncertainty interval with 95\% confidence was computed for
$C_P$, $C_D$, and mean wake velocities
\begin{equation}
    U_{95} = t_{95} u_c,
\end{equation}
where $t_{95}$ is the value from the Student-$t$ distribution for a 95\%
confidence interval and $u_c$ is the combined standard uncertainty. Combined
standard uncertainty for a given quantity $X$ is calculated by
\begin{equation}
    u_X^2 = s_{\bar{X}}^2 + b_X^2,
\end{equation}
where $s_{\bar{X}}$ is the sample standard deviation of the mean per turbine
revolution, and $b_X$ is the systematic uncertainty, computed by
\begin{equation}
    b_{X}^2 = \sum_{i=1}^J \left( \frac{\partial X}{\partial x_i} \right)^2
    b_{x_i}^2,
\end{equation}
where $x_i$ is a primitive quantity used to calculate $X$ (e.g. $T$, $\omega$,
and $U_\infty$ for calculating $C_P$), and $b_{x_i}$ is the primitive quantity's
systematic uncertainty, estimated as half the value listed on the sensor
manufacturer's documentation.

Selecting $t_{95}$ requires an estimate for degrees of freedom $\nu_X$, which
was obtained using the Welch--Satterthwaite formula
\begin{equation}
    \nu_X = \frac{\left(s_X^2 + \sum_{k=1}^M b_k^2 \right)^2} {s_X^4/\nu_{s_X} +
    \sum_{k=1}^M b_k^4/\nu_{b_k}},
\end{equation}
where $\nu_{s_X}$ is the number of degrees of freedom associated with $s_X$ and
$\nu_{b_k}$ is the number of degrees of freedom associated with $b_k$.
$\nu_{s_X}$ is assumed to be $(N-1)$, where $N$ is the number of independent
samples (or turbine revolutions). $\nu_{b_k}$ was estimated as
\begin{equation}
    \nu_{b_k} = \frac{1}{2} \left( \frac{\Delta b_k}{b_k} \right)^{-2},
\end{equation}
where the quantity in parentheses is the relative uncertainty of $b_k$, assumed
to be 0.25.

For the Reynolds number dependence of turbine performance, error bars are
included on the plots. Expanded uncertainty estimates for mean wake velocities
(averaged over all runs) are listed in Table~\ref{tab:vel-unc}.

\begin{table}
    \centering
\begin{tabular}{cccc}
$U_\infty$ (m/s) &                $U$ &                $V$ &                $W$ \\
\hline
           $0.4$ & $1 \times 10^{-2}$ & $7 \times 10^{-3}$ & $6 \times 10^{-3}$ \\
           $0.6$ & $1 \times 10^{-2}$ & $8 \times 10^{-3}$ & $8 \times 10^{-3}$ \\
           $0.8$ & $2 \times 10^{-2}$ & $1 \times 10^{-2}$ & $1 \times 10^{-2}$ \\
           $1.0$ & $2 \times 10^{-2}$ & $1 \times 10^{-2}$ & $1 \times 10^{-2}$ \\
           $1.2$ & $2 \times 10^{-2}$ & $1 \times 10^{-2}$ & $1 \times 10^{-2}$ \\
\end{tabular}
\caption{Average expanded uncertainty estimates (with 95\% confidence) for mean
    velocity measurements at each tow speed.}

\label{tab:vel-unc}
\end{table}
